A Multi-Modal Model of Object Deformation for Robotics

### 2016-09-06 twostagedo.tex
small change to model overview, fixed missing cross reference

\comment{The two learned models, FP and SP, can be sequenced to create a single, multi-modal predictor (Figure~\ref{ig:prediction}). This combined model takes a planned motion of the finger, and predicts the resulting forces experienced. It then uses both the position and forces to predict the resulting object deformation. Typically a sequence of planned finger positions will be known. In prediction mode the models make predictions based on this sequence. To create the prediction for time $t+1$ the previous predicted state at time $t$ is required: thus the predictions are recursive. This enables predictions over arbitrarily long time periods, but makes learning a good predictor challenging.}

@@

The training of the model is performed offline using ground truthed data. %The overall algorithm is given in \alref{alg:overall}.
For clarity the algorithm is given in three phases: training, simulation (i.e. the prediction phase), and classification (i.e. matching prediction to new data). In testing the model new data is used, where this is typically new deformation actions on an object of known material and approximate shape. Having given an overview of the model we now relate our approach to those in the literature, before proceeding to describe the details of the spring-mass model of deformation (Section~\ref{sec:model}), and then the regression model of contact forces (Section~\ref{sec:forces}).

>>>>

\comment{The two learned models, FP and SP, can be sequenced to create a single, multi-modal predictor (Figure~\ref{fig:prediction}). This combined model takes a planned motion of the finger, and predicts the resulting forces experienced. It then uses both the position and forces to predict the resulting object deformation. Typically a sequence of planned finger positions will be known. In prediction mode the models make predictions based on this sequence. To create the prediction for time $t+1$ the previous predicted state at time $t$ is required: thus the predictions are recursive. This enables predictions over arbitrarily long time periods, but makes learning a good predictor challenging.}

@@

%The training of the model is performed offline using ground truthed data. %The overall algorithm is given in \alref{alg:overall}.
For clarity the algorithm is described in exactly these three phases: training, simulation (i.e. the prediction phase), and classification. In empirically evaluating the model new data was used, acquired from new finger pushes. We now proceed to describe the shape predictor SP (Section~\ref{sec:model}) which is based on a mass-spring system, and then the force predictor (FP), which is a regression model (Section~\ref{sec:forces}).
